Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-09-30 WSSSPE3/report/wg_appendix_publishing_SW.tex
Update member affiliations.
Former-commit-id: 6d0b2140887bc8c5403be56880d5009b438a21cd
Fix compile problem.
Former-commit-id: 79bddccfbde22d98d3af9e93bcb9f9581bf36a81
Fleshed out main section.
Former-commit-id: 88d5f396cbab1b88397c525cf3d98b376faff1e3

\subsection{Group Members}
{\small
\begin{longtable}{ll}
   Steven R. Brandt & Louisiana State University
\\ Daniel Gunter    & 
\\ Yuhan Ding       & 
\\ Neil Chue Hong   & Software Sustainability Institute
\end{longtable}
}

@@

This group explored the value of executable papers (papers whose content includes
the code needed to produce their own results), and other forms of publishing which
include dynamic electronic content. Transitioning to this type of publication offers
possibilities of addressing, or partially addressing sustainability concerns 
such as reproducibility (the paper contains all the artifacts needed to verify its
results), transitive credit (modules an executable paper depends on must be explicitly
loaded, making it more feasible to identify them), and improving documentation (an executable
paper must explain what its code does).

While the group did not feel it had a way to influence what is currently happening
in these experimental publishing venues, it felt that creating and curating a list of
such efforts would have value by attracting interest to these activities.
The Software Sustainability Institute agreed to host this list.

A tentative first cut at the list contains the following:
\begin{enumeration}
\item ACM Transactions on Mathematical Software (TOMS) - which provides the extra step
 of having reviewers validate the code which was submitted with the publication.
\item The Mathematica Journal - which publishes Mathematica notebooks (with equations,
figures, etc.) directly.
\item O'Reily Media has announced that it plans to make IPython Notebooks a first-class
 authoring environment for their publishing program alongside their existing mechanisms.
\item Nature is offering a list of notebooks published alongside more traditional articles,
 and is looking at ways to make these documents more official. There are, in fact, a
 number of journals that offer "electronic supplements" to the more traditionally published
 static articles.
\item There is also a list of "reproducible academic publications" maintained here:
  \url{https://github.com/ipython/ipython/wiki/A-gallery-of-interesting-IPython-Notebooks#reproducible-academic-publications}
\end{enumeration}

>>>>

\subsection{Group Members}
{\small
\begin{longtable}{ll}
   Steven R. Brandt & Louisiana State University
\\ Daniel Gunter    & LBNL
\\ Yuhan Ding       & Illinois Institute of Technology
\\ Neil Chue Hong   & Software Sustainability Institute
\end{longtable}
}

@@

A tentative first cut at the list contains the following:
\begin{itemize}
\item ACM Transactions on Mathematical Software (TOMS) - which provides the extra step
 of having reviewers validate the code which was submitted with the publication.
\item The Mathematica Journal - which publishes Mathematica notebooks (with equations,
figures, etc.) directly.
\item O'Reily Media has announced that it plans to make IPython Notebooks a first-class
 authoring environment for their publishing program alongside their existing mechanisms.
\item Nature is offering a list of notebooks published alongside more traditional articles,
 and is looking at ways to make these documents more official. There are, in fact, a
 number of journals that offer "electronic supplements" to the more traditionally published
 static articles.
\item There is also a list of "reproducible academic publications" maintained here:
  \url{https://github.com/ipython/ipython/wiki/A-gallery-of-interesting-IPython-Notebooks#reproducible-academic-publications}
\end{itemize}
